Assignment 2

### 2025-03-13 code/Reddit_API.qmd
updated data

library(tidyverse)
library(writexl)
# install.packages("devtools")
# devtools::install_github('ivan-rivera/RedditExtractor')
library(RedditExtractoR)
```

@@

```{r}
reddit_unclean <- readRDS("~/repos/SURV622_Assignment/data/posts_data.RDS")
glimpse(reddit_unclean)
```

@@

-   We listened for five days every hour, yet we needed to add additional posts as we did not have enough. Instead, we add posts starting from 2/24/25 when the project started. This way we have almost \~900 posts after cleaning the found data set.

@@

reddit_clean <- reddit_unclean |>
  # set timeline threshold 
  filter(date_utc > "2025-02-25") |> 
  # function we created
   tibble() |> 
    # remove any duplicates
  distinct() |> 
   mutate(
          # remove urls from text using rm_url function
      text = qdapRegex::rm_url(text),
      date_utc = ymd(date_utc) ) |> 
   filter(# remove none related topic threads
           !str_detect(text, "crypto|coin"))

glimpse(reddit_clean)
```

@@

```{r}
# pass the urls collected from the post
reddit_content <- map(reddit_clean$url, function(x){

  thread = get_thread_content(x)

@@

-   Separate post metadata and merge as new columns into the clean reddit data set we extracted from our initial data collection.

@@

# add new columns to our working data
reddit_clean <- reddit_clean |> 
  add_column(reddit_metadata |> 
               select(score:cross_posts))
```

@@

  # pass the list element that houses comments
  x$comments |> 
    tibble() |> 
    mutate_all(as.character)
}
) |> 
  # ger rid of NULL, no comments
  discard(is_null) |>
  # put data in data frame structure
  bind_rows() |> 
  # remove duplicates
  distinct() |> 
  # retain variable types
  mutate(
    # remove URL links
    comment = qdapRegex::rm_url(comment),
    date = ymd(date), 
    timestamp = as.double(timestamp),
    # if no text in comment, code as NA
    comment = na_if(comment, "")) |> 
  rename(date_utc = date) |> 
  filter(!is.na(comment),
         # remove none related topic threads
         !str_detect(comment, "crypto|coin"),#,
         # drop text that are one or two words
         str_count(comment, " ") >= 12
  )

@@

```{r}
reddit_comments <- reddit_comments |> 
  left_join(
    # select needed variables
    reddit_clean |> 
      select(url, subreddit, search_term),
    relationship = "many-to-many"
  )

@@

We want to do some additional cleaning to the posts dataset. Ideally, we want to remove empty or short text.

```{r}
reddit_clean <- reddit_clean |> 
  mutate(text = na_if(text, "")) |> 
   filter(!is.na(text),
         # drop text that are one or two words
         str_count(text, " ") >= 12
  )

@@

```{r}
# write posts data
writexl::write_xlsx(reddit_clean, "D:/repos/SURV622_Assignment/data/posts_data_clean.xlsx")

# write comments data
writexl::write_xlsx(reddit_comments, "D:/repos/SURV622_Assignment/data/comments_data_clean.xlsx")

>>>>

library(writexl)
library(fedmatch)
# install.packages("devtools")
# devtools::install_github('ivan-rivera/RedditExtractor')
library(RedditExtractoR)
library(tidyverse)

@@

```{r}
reddit_unclean <- readRDS("~/repos/SURV622_Assignment/data/posts_data.RDS")

@@

-   We listened for five days every hour, yet we needed to add additional posts as we did not have enough. Instead, we add posts starting from 2/24/25 when the project started. This way we have almost \~900 posts after cleaning the found data set.
-   Note. Some posts are related meaning that the more than one keyword may show up. Identify the duplicates, and just keep one. We don't really care for keyword search after this point, so we can drop it.

@@

reddit_post <- reddit_unclean |>
  # set timeline threshold 
  filter(date_utc > "2025-03-01") |> 
  # function we created
   tibble() |> 
   mutate(
          # remove urls from text using rm_url function
      text = qdapRegex::rm_url(text),
      # clean text from unwanted character
      text = clean_strings(text),
      date_utc = ymd(date_utc) ) |> 
   filter(# remove none related topic threads
           !str_detect(text, "crypto|coin")) |> 
  # drop duplicates
  distinct_at(vars(-search_term, -comments))

  # bring back search terms
reddit_post <- reddit_post |> 
  left_join(
    reddit_unclean |> 
      group_by(comments) |> 
      filter(comments == max(comments)) |> 
      group_by(url) |> 
      mutate(id = row_number()) |> 
      # keep first of x number of posts
      filter(id==min(id)) |> 
      select(url, search_term, comments)
    )

@@

```{r}
# pass the urls collected from the post
reddit_content <- map(seq_along(reddit_post$url), function(x){

  print(x)

  thread = get_thread_content(reddit_post$url[x])

@@

-   Separate post metadata and merge as new columns into the reddit posts data set we extracted from our initial data collection.
-   We need a column that can join posts with comments. Currently, the URL column can do this but it is long. Let's assign a unique ID while enriching this dataset.

@@

# add new columns to our working data
reddit_post <- reddit_post |> 
  add_column(reddit_metadata |> 
               select(score:cross_posts)) |> 
  arrange(date_utc) |>
  # assign IDs to posts
  mutate(post_id = row_number())
```

@@

  # pass the list element that houses comments
  x$comments |> 
    tibble() |> 
    mutate_all(as.character)
}
) |> 
  # ger rid of NULL, no comments
  discard(is_null) |>
  # put data in data frame structure
  bind_rows() |> 
  # remove duplicates
  distinct() |> 
  # retain variable types
  mutate(
    # remove URL links
    comment = qdapRegex::rm_url(comment),
    # clean comment strings
    comment = clean_strings(comment),
    date = ymd(date), 
    timestamp = as.double(timestamp),
    # if no text in comment, code as NA
    comment = na_if(comment, "")) |> 
  rename(date_utc = date) |> 
  filter(!is.na(comment),
         # remove none related topic threads
         !str_detect(comment, "crypto|coin"),#,
         # drop text that are one or two words
         str_count(comment, " ") >= 12
  )

@@

```{r}
reddit_comments <- reddit_comments |> 
  left_join(
    # select needed variables
    reddit_post |> 
      select(url, subreddit, search_term, post_id)
  )

@@

```{r}
# write posts data
writexl::write_xlsx(reddit_post, "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx")

# write comments data
writexl::write_xlsx(reddit_comments, "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx")

@@
